Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-08-09 manuscript/manuscript.Rmd
Last commit before signing off

There are a number of questions that we have left unanswered that we hope will be addressed in future work.
In this paper, we have explored a small number of machine learning and statistical models that can be used for forecasting, so comprehensive conclusions can not be drawn on whether statistical or machine learning-based approaches are better suited for tipping point forecasting problems.
Neither can we claim that the ML methods employed will translate well to all sudden transition event forecasting problems in reality, since working with real data will introduce additional difficulties like how to deal with missing data, sparse data or observation error.

@@

Ecological forecasting is invariably difficult, even in the idealized cases of ample measurement data and clearly identified structural models.
This paper is not intended to give a complete answer to whether machine learning models are the the best methods to use on any tipping point forecasting problem as this will take numbers of studies to resolve; instead, this study aims to be an early exploration on whether deep learning methods should be considered as viable tools for this extremely challenging class of forecasting problems.
Since we have shown that ML models can make good forecasts on our selected tipping point scenarios, particularly the stochastic transition case, we have established that these deep learning models are promising methods for critical transition forecasting problems.

>>>>

There are a number of questions that we have left unanswered that we hope will be addressed in future work.
In this paper, we have explored a small number of machine learning and statistical models that can be used for forecasting, so comprehensive conclusions can not be drawn on whether statistical or machine learning-based approaches are better suited for tipping point forecasting problems.
Neither can we claim that the ML methods employed will translate well to all sudden transition event forecasting problems in reality, since working with real data will introduce additional difficulties like how to deal with missing data, sparse data and observation errors.

@@

Ecological forecasting is invariably difficult, even in the idealized cases of ample measurement data and clearly identified structural models.
This paper is not intended to give a complete answer to whether deep learning is the best suited method for tipping point forecasting problems as this will take numerous studies to resolve; instead, this study aims to be an early exploration on whether deep learning methods should be considered as viable tools for this extremely challenging class of prediction problems. <!-- I think here would perhaps be a good place to flesh out "promising" tag, stuck on how to do so-->
Since we have shown that ML models can make good forecasts on our selected tipping point scenarios, particularly the stochastic transition case, we have established that these deep learning models are promising methods for critical transition forecasting problems.
